Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-06-13 paper.tex
updates

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres.pdf}
}
\caption{ Angular resolutions as functions of the incidence angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$ (b) }
\label{fig:angle_reco_dep_gr}
\end{figure}

@@

We tune the hyperparameter of the XGB to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration. We find that 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$. We also conclude that using 24 front layers gives the acceptable angular resolution of 1.33~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer. We evaluate angular resolutions in terms of the incidence angle and the incident energy. The angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$. $p_{0}$ is estimated to be 0.43$^{\circ}$ and not dependent on the incidence angle. $p_{1}$ is estimated to be 1.28--1.04$^{\circ}$ and gradually decreasing with the incidence angle.

Furthermore, we study that the angular resolution is changing with the variation of the training of the XGB and the detector configuration. As the strip width decreases, more channels of scintillator strips are required, and the training of the XGB gets affected due to the increased feature size. This is quenched with the larger number of training samples, which qualitatively improves the training of the XGB. On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse. We conclude that 15-mm-wide strips provide the favorable angular resolution with 24 front layers and $10^{5}$ training samples.

>>>>

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.44\textwidth]{figures/Fig7_res_ene.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{
\includegraphics[width=0.5\textwidth]{figures/Fig7_Fit_eres_1.pdf}
}
\caption{ Angular resolutions as functions of the incidence angle for different incident energies (a) and the incident energy for $\theta=$~25$^{\circ}$, which is fitted with $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$ (b) }
\label{fig:angle_reco_dep_gr}
\end{figure}

@@

We tune the hyperparameter of the XGB to reconstruct the incidence angle with the best angular resolution, and study the angular resolution in terms of the detector configuration. We find that 15-mm-wide strips provide the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$. We also conclude that using 32 front layers gives the acceptable angular resolution of 1.30~$\pm$~0.01$^{\circ}$, which is only 0.1$^{\circ}$ higher than the angular resolution we get from the full layer. We evaluate angular resolutions in terms of the incidence angle and the incident energy. The angular resolution can be expressed as $p_{0} \oplus p_{1}/\sqrt{E_{\gamma}(GeV)}$. For large incidence angle ($\theta>$~10~deg), $p_{0}$ and $p_{1}$ are estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. The angular resolution is largely dependent on the incidence angle for the low incident energy, resulting in smaller values for $p_{1}$.

Furthermore, we study that the angular resolution is changing with the variation of the training of the XGB and the detector configuration. As the strip width decreases, more channels of scintillator strips are required, and the training of the XGB gets affected due to the increased feature size. This is quenched with the larger number of training samples, which qualitatively improves the training of the XGB. On the other hand, the longer strip width provides the worse angular resolution as the position resolution of the EM shower gets worse. We conclude that 15-mm-wide strips provide the favorable angular resolution with 32 front layers and $10^{5}$ training samples.
